### 2021-06-22 results.tex
logistic regression for the first study

Altogether, ignoring  \joke, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of the
DroidFax static analysis algorithms. Besides that, in the first execution (WS), none of the
resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
At this point, an additional question arises: what are the characteristics
of the malwares that have (not) been identified using the mining sandbox approach?
To explore this question, we take advantage of the
\texttt{dex2jar} tool to reverse-engineer all 96 malwares considered in our analysis and
computed the \emph{diffs} of the benign/malicious versions of the APPs.
The results of this activity are available in our replication
package.\footnote{https://github.com/droidxp/paper-replication-package/blob/master/diff/} 
In what follows we dissect a few examples of malwares
that at least one dynamic analysis tool was able to
identify using the mining sandbox approach. After that,
we present the characteristics of a malware that none of the tools
was able to detect. Our goal here is to provide
a lower-level intuition about the classes of malware the
mining sandbox approach is able to detect. A reader that
is not interested in these details could skip to
Section~\ref{sec:res-ss}.

>>>>

Altogether, ignoring  \joke, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of the
DroidFax static analysis algorithms. We also investigate if the use
of the DroidFax static analysis component is statistically significant to identify
malwares in our experiment. To this end, we build a logistic regression model
in the form $Malware \sim Tool + StaticAnalysis + Repetition$. Table~\ref{tab:log-reg1}
shows the results of the logistic regression analysis, highlighting the
Humanoid has a negative and significant impact on malware identification and
the use of DroidFax static analysis has a positive and significant
impact on malware identification.

\begin{table}[ht]
  \centering
     \caption{Results of the Logistic Regression} 
       \begin{small}
     \begin{tabular}{lrlc}
   \toprule
  & \emph{Estimate} & \emph{p-value} & \emph{C.I.} \\ 
   \midrule
   Tool [DroidBot] & 0.1034 & 0.4718 & (-0.133$, $0.340) \\ 
   Tool [DroidMate] & -0.0561 & 0.6955 & (-0.292$, $0.180) \\ 
   Tool [Humanoid] & -0.8910  & 0.0000 $^{***}$ & (-1.131$, $-0.651) \\ 
   Tool [Monkey] & -0.0110 & 0.9390 &  (-0.247$, $0.225)\\ 
   DroidFax static analysis & 0.8867 & 0.0000 $^{***}$ & (0.743$, $1.031)\\ 
   Repetition & -0.0171 & 0.7487 & (-0.105$, $0.071) \\ \midrule
   AIC            & 3001.07     \\
   Num. obs.      & 2304        \\
   \bottomrule
   \multicolumn{4}{l}{\scriptsize{$^{***}$ \emph{p-value} $<0.001$}}
     \end{tabular}
        \end{small}

    \label{tab:log-reg1} 
\end{table}

Besides that, in the first execution (WS), none of the
resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.
At this point, an additional question arises: what are the characteristics
of the malwares that have (not) been identified using the mining sandbox approach?
To explore this question, we take advantage of the
\texttt{dex2jar} tool to reverse-engineer all 96 malwares considered in our analysis and
computed the \emph{diffs} of the benign/malicious versions of the APPs.
The results of this activity are available in our replication
package.\footnote{https://github.com/droidxp/paper-replication-package/blob/master/diff/} 
In what follows we dissect a few examples of malwares
that at least one dynamic analysis tool was able to
identify using the mining sandbox approach. After that,
we present the characteristics of a malware that none of the tools
was able to detect. Our goal here is to provide
a lower-level intuition about the classes of malware the
mining sandbox approach is able to detect. A reader that
is not interested in these details could skip to
Section~\ref{sec:res-ss}.

### 2021-06-22 setup.tex
logistic regression for the first study

To sum up, in order to analyse the
performance of the test case generation tools (including Joker),
we just have to compare the calls to sensitive APIs made by
the benign and malign versions of the apps, during
the execution of the tools. We then use descriptive statistics
and plots to compare the performance of the tools and
answer RQ1 and RQ2.

>>>>

To sum up, in order to analyse the
performance of the test case generation tools (including Joker),
we just have to compare the calls to sensitive APIs made by
the benign and malign versions of the apps, during
the execution of the tools. In the end, we generate
a set of observations, where each observation
contains the tool name, the number of the repetition (in the
range [1..3]), a boolean value reporting the use of the
DroidFax static analysis component, and a boolean value indicating
whether or not the malware has been identified. We use descriptive statistics
and plots to compare the performance of the tools and
answer RQ1 and RQ2. We also use \emph{Logistic Regression} to understand
the relevance of the features (tool, repetition, DroidFax static analysis
component) to predict the malware identification.
